Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-08-30 paper/paper.tex
Prop 2, Cor 1, Defns, Proofs

Let $S$ and $T$ be two sequences. We define $S \preceq T$

\todo{Define $\preceq$, deg, nds}

@@

\begin{proposition}
    More powerfully, if $p \lessmap t$ then
    $(\nds(p)[k+1] - k, \nds(p)[k+2] - k, \ldots) \preceq \nds(t)$.
\end{proposition}

\begin{proof}
Let

\end{proof}
\begin{figure}
    \begin{center}
        \begin{tikzpicture}[every node/.style={circle, inner sep=1mm}]
            \node[fill=black] (p) {};
            \node[draw=none,right of = p,node distance=3mm,yshift=-1mm] {$p$};
            \node[fill=uofglawn] (n2) [above of = p,node distance=12mm] {};
            \node[fill=uofgpumpkin] (n1) [left of = n2] {};
            \node[fill=uofglawn] (n3) [right of = n2] {};
            \node[fill=uofgcobalt] (q) [above of = n2,node distance=12mm] {};
            \path (p) edge (n1) edge (n2) edge (n3)
                (n1) edge (q)
                (n2) edge (n3) edge (q)
                (n3) edge (q);
        \end{tikzpicture}
        \caption{Graph that Craig wanted}
        \label{fig:nds}
    \end{center}
\end{figure}

>>>>

Let $p$ be a vertex in a graph $P$, the \emph{degree} of $p$, $\deg(p)$, is the number of vertices
to which it is adjacent

@@

A vertex $q$ which is adjacent to $p$ is called its \emph{neighbour}.  Let $N(p) = \{ q \in V_p | p
\text{ and } q \text{ are adjacent }\}$ be the set of neighbours of $p$.  The \emph{neighbourhood
degree sequence} (NDS) of $p$, $\nds(p)$, is the (non-ascending) sequence of degrees of its
neighbours.

Let $S = ( s_1 , \ldots , s_n )$ and $T = ( t_1 , \ldots , t_m)$ be two sequences.  We say that $S
\preceq T$ if $n \leq m$ and $\forall s_i \in S$ there exists a distinct $t_j \in T$ with $s_i \leq
t_j$.  (When considering a $k$-less-subgraph isomorphism) we say that $S \prescript{}{k}{\preceq}
T$ if $n - k \leq m$ and $\forall s_i \in S \setminus S_k$, where $S_k$ is a subsequence of $S$
containing up to $k$ members of $S$, there exists a distinct $t_j \in T$ with $s_i - k \leq t_j$.

\begin{proposition}
If $p \prescript{}{k}{\mapsto} t$, then $\nds(p) \prescript{}{k}{\preceq} \nds(t)$.
\end{proposition}

\begin{proof}
Let $p \prescript{}{k}{\mapsto} t$.  Then $\deg(p) - k \leq \deg(q)$, by Proposition 1, which
implies that $|\nds(p)| -k \leq |\nds(t)|$.

Also, $p \prescript{}{k}{\mapsto} t$ implies that for each $q \in N(p)\setminus P_k$, where $P_k$
is some subset of $P$ with $|P_k| \leq k$, $q \prescript{}{k}{\mapsto} u$, where $u \in N(t)$ and
each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by Proposition 1.  Hence $\nds(p)
\prescript{}{k}{\preceq} \nds(t)$.
\end{proof}

Figure\ref{fig:nds} illustrates the three cases possible when filtering by neighbourhood degree
sequence.  Removing the top node causes each entry in $\nds(p)$ to be reduced; removing the 
left-middle node removes an entry from $\nds(p)$; and removing either of the connected nodes in the
middle layer causes both the size of $\nds(p)$ to be reduced and an entry in $\nds(p)$ to be reduced.

\begin{corollary}
You can just ignore the first K things in $\nds(p)$, assuming it's ordered.
\end{corollary}

\begin{proof}
Do we need this?
\end{proof}

\begin{figure}
    \begin{center}
        \begin{tikzpicture}[every node/.style={circle, inner sep=1mm}]
            \node[fill=black] (p) {};
            \node[draw=none,right of = p,node distance=3mm,yshift=-1mm] {$p$};
            \node[fill=uofglawn] (n2) [above of = p,node distance=12mm] {};
            \node[fill=uofgpumpkin] (n1) [left of = n2] {};
            \node[fill=uofglawn] (n3) [right of = n2] {};
            \node[fill=uofgcobalt] (q) [above of = n2,node distance=12mm] {};
            \path (p) edge (n1) edge (n2) edge (n3)
                (n1) edge (q)
                (n2) edge (n3) edge (q)
                (n3) edge (q);
        \end{tikzpicture}
        \caption{Graph that Craig wanted}
        \label{fig:nds}
    \end{center}
\end{figure}
